Search-based Synthesis of Network Intrusion Detection Rules

### 2019-10-02 paper/paper.tex
pass on evaluation

>>>>

\Gui{We are using the bigflows.pcap provided by tcpreplay on http://tcpreplay.appneta.com/wiki/captures.html "This is a capture of real network traffic on a busy private network’s access point to the Internet"
We also used normal pcaps from Stratosphere Lab on https://www.stratosphereips.org/datasets-normal to verify if Suricata's ET rules weren't catching positive flow. }
